 ---
title: "Gun Control Chi-Square"
author: "Kristan Culbert"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Kristan and I'm adding text here to see if my collaborators can get this file. 

It's Kristan again and I'm updating some text. 

Today is Wednesday and I'm very excited that tomorrow is Thursday because that means it's almost Friday :D

Dunno about you, but I'm planning to sleep in this weekend!!! #yass

Creator (Kristan): 

Getting gc_df.csv data, loading the tidyverse, and getting some summary counts

```{r}

# Loading tidyverse, loading in data, getting summary counts

library(tidyverse)
gc_df <- read_csv("gc_df.csv")

#Count function allows you to set groupings for categorical variables
#Spread function allows you to spread a key-value pair across multiple columns.

get_guns <- gc_df %>% 
  filter(gender !="NA", make_get_guns !="NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <-c("Female", "Male")
  
```

Collaborator: Tyanna Bui

Doing Chi-Squared - Is there a sig association between sex and gun control recommendations?

```{r}
# calculates prop of cell/whole table... ", 1" calculates by row & storing as matrix (as.matrix)
guns_prop = prop.table(as.matrix(get_guns), 1) 
guns_prop

# performing chi-squared
guns_x2 = chisq.test(get_guns)
guns_x2 # p-value < 2.2e-16

```

Recommended government action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001).

Point of why this is.. explain interesting observations from the table to help audience understand.






