 ---
title: "Gun Control Chi-Square"
author: "Kristan Culbert"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Kristan and I'm adding text here to see if my collaborators can get this file. 

It's Kristan again and I'm updating some text. 

Today is Wednesday and I'm very excited that tomorrow is Thursday because that means it's almost Friday :D

Dunno about you, but I'm planning to sleep in this weekend!!! #yass

Creator (Kristan): 

Getting gc_df.csv data, loading the tidyverse, and getting some summary counts

```{r}

# Loading tidyverse, loading in data, getting summary counts

library(tidyverse)
gc_df <- read_csv("gc_df.csv")

#Count function allows you to set groupings for categorical variables
#Spread function allows you to 

get_guns <- gc_df %>% 
  filter(gender !="NA", make_get_guns !="NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <-c("Female", "Male")
  

```

